Taking Linear Logic Apart

### 2019-06-14 doc/paper/main.tex
small fix to H-Cut

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018}
\usepackage{url,doi}
\usepackage[british]{babel}
\usepackage[all]{foreign}
\usepackage{amsmath,amsthm,amssymb}
\allowdisplaybreaks
\def\Coloneqq{\mathbin{::=}}
\def\coloneqq{\mathbin{:=}}
\usepackage[inline]{enumitem}%
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{textcomp,textgreek,upgreek,stmaryrd}
\usepackage{nameref,hyperref}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{scalerel}
\usepackage{rotating}
\usepackage{centernot}
\usepackage{xspace}
\xspaceaddexceptions{]\}}
\usepackage[nameinlink,noabbrev,capitalize]{cleveref}
\hypersetup{hidelinks,final}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{definition}[lemma]{Definition}
\input{preamble-typing}
\usepackage[sectionbib,sort&compress,numbers]{natbib}

@@

Typing judgements in \hcp associate processes with hyper-environments. \textsc{H-Mix} composes two processes in parallel, but remembers that they are independent in the sequent. \textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar. Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''. This prevents self-locking processes, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
\begin{definition}[Typing judgements]\label{def:hcp}
  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$. 
  Typing judgements can be constructed using the inference rules below. 
  \\[1\baselineskip]
  {Structural rules} %\vspace{-3ex}
  \begin{center}
    \hcpInfAx
    \hcpInfCut
  \end{center}
  \begin{center}
    \hcpInfMix
    \hcpInfHalt
  \end{center}
%  \vspace{.3ex}
  {Logical rules} %\vspace{-3ex}
  \begin{center}
    \hcpInfBoundTens
    \hcpInfParr
  \end{center}
  \begin{center}
    \hcpInfOne
    \hcpInfBot
  \end{center}
  \begin{center}
    \hcpInfPlus1
    \hcpInfPlus2
  \end{center}
  \begin{center}
    \hcpInfWith
  \end{center}
  \begin{center}
    \hcpInfNil
    \hcpInfTop
  \end{center}
\end{definition}
Note that the logical rules disallow hyperenvironments. If they did not, the following processes would be well-typed, even though they are stuck (unless we allow delayed actions as in \dhcp):
\begin{center}
  \begin{prooftree*}
    \noLine\AXC{$\vphantom{\Gamma}$}\UIC{$\vphantom{\Gamma}$}
    \NOM{H-Mix$_0$}
    \UIC{$\seq
      [\piHalt]
      {\emptyhypercontext}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{z}{}{\piHalt}]
      {\tmty{z}{\one}}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}]
      {\tmty{x}{\one} \hsep \tmty{z}{\one}}$}
    \SYM{(\bot)}
    \UIC{$\seq
      [\piRecv{x}{}{\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}}]
      {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
    \NOM{Cut}
    \UIC{$\seq
      [\piNew{x}{(\piRecv{x}{}{\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}})}]
      {\tmty{z}{\one}}$}
  \end{prooftree*}\hspace*{-1.75em}%
  \begin{prooftree*}
    \AXC{}
    \NOM{H-Mix$_0$}
    \UIC{$\seq
      [{\piHalt}]
      {\emptyhypercontext}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{y}{}{\piHalt}]
      {\tmty{y}{\one}}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}]
      {\tmty{x}{\one} \hsep \tmty{y}{\one}}$}
    \AXC{}
    \NOM{Ax}
    \UIC{$\seq
      [\cpLink{x}{z}]
      {\tmty{x}{\bot}, \tmty{z}{\one}}$}
    \SYM{(\bot)}
    \UIC{$\seq
      [\piRecv{y}{}{\cpLink{x}{z}}]
      {\tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
    \NOM{H-Mix}
    \BIC{$\seq
      [(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})]
      {\tmty{x}{\one} \hsep \tmty{y}{\one} \hsep \tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
    \NOM{Cut}
    \UIC{$\seq
      [\piNew{y}{(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})}]
      {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
    \NOM{Cut}
    \UIC{$\seq
      [\piNew{x}{\piNew{y}{(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})}}]
      {\tmty{z}{\one}}$}
  \end{prooftree*}
\end{center}\vspace{.5\belowdisplayskip}

>>>>

\documentclass[copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018}
\usepackage{url,doi}
\usepackage[british]{babel}
\usepackage[all]{foreign}
\usepackage{amsmath,amsthm,amssymb}
\allowdisplaybreaks
\def\Coloneqq{\mathbin{::=}}
\def\coloneqq{\mathbin{:=}}
\usepackage[inline]{enumitem}%
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{textcomp,textgreek,upgreek,stmaryrd}
\usepackage{nameref,hyperref}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{scalerel}
\usepackage{rotating}
\usepackage{centernot}
\usepackage{xspace}
\xspaceaddexceptions{]\}}
\usepackage[nameinlink,noabbrev,capitalize]{cleveref}
\hypersetup{hidelinks,final}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{definition}[lemma]{Definition}
\input{preamble-typing}
\usepackage[sectionbib,sort&compress,numbers]{natbib}

\usepackage[framemethod=tikz]{mdframed}
\newenvironment{changed}
	{\mdframed[hidealllines=true,backgroundcolor=black!20]}
	{\endmdframed}

@@

Typing judgements in \hcp associate processes with hyper-environments. \textsc{H-Mix} composes two processes in parallel, but remembers that they are independent in the sequent. \textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar (the side condition $\tm{x} \not\in \ty{\mathcal{G}}$ ensures that sessions are binary). 
%This prevents self-locking processes, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
\begin{definition}[Typing judgements]\label{def:hcp}
  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$. 
  Typing judgements can be constructed using the inference rules below. 
  \\[1\baselineskip]
  {Structural rules} %\vspace{-3ex}
  \begin{center}
    \hcpInfAx
    \hcpInfCut
  \end{center}
  \begin{center}
    \hcpInfMix
    \hcpInfHalt
  \end{center}
%  \vspace{.3ex}
  {Logical rules} %\vspace{-3ex}
  \begin{center}
    \hcpInfBoundTens
    \hcpInfParr
  \end{center}
  \begin{center}
    \hcpInfOne
    \hcpInfBot
  \end{center}
  \begin{center}
    \hcpInfPlus1
    \hcpInfPlus2
  \end{center}
  \begin{center}
    \hcpInfWith
  \end{center}
  \begin{center}
    \hcpInfNil
    \hcpInfTop
  \end{center}
\end{definition}
Note that the logical rules disallow hyperenvironments. If they did not, the following processes would be well-typed, even though they are stuck (unless we allow delayed actions as in \dhcp):
\begin{center}
  \begin{prooftree*}
    \noLine\AXC{$\vphantom{\Gamma}$}\UIC{$\vphantom{\Gamma}$}
    \NOM{H-Mix$_0$}
    \UIC{$\seq
      [\piHalt]
      {\emptyhypercontext}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{z}{}{\piHalt}]
      {\tmty{z}{\one}}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}]
      {\tmty{x}{\one} \hsep \tmty{z}{\one}}$}
    \SYM{(\bot)}
    \UIC{$\seq
      [\piRecv{x}{}{\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}}]
      {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
    \NOM{Cut}
    \UIC{$\seq
      [\piNew{x}{(\piRecv{x}{}{\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}})}]
      {\tmty{z}{\one}}$}
  \end{prooftree*}\hspace*{-1.75em}%
  \begin{prooftree*}
    \AXC{}
    \NOM{H-Mix$_0$}
    \UIC{$\seq
      [{\piHalt}]
      {\emptyhypercontext}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{y}{}{\piHalt}]
      {\tmty{y}{\one}}$}
    \SYM{(\one)}
    \UIC{$\seq
      [\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}]
      {\tmty{x}{\one} \hsep \tmty{y}{\one}}$}
    \AXC{}
    \NOM{Ax}
    \UIC{$\seq
      [\cpLink{x}{z}]
      {\tmty{x}{\bot}, \tmty{z}{\one}}$}
    \SYM{(\bot)}
    \UIC{$\seq
      [\piRecv{y}{}{\cpLink{x}{z}}]
      {\tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
    \NOM{H-Mix}
    \BIC{$\seq
      [(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})]
      {\tmty{x}{\one} \hsep \tmty{y}{\one} \hsep \tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
    \NOM{Cut}
    \UIC{$\seq
      [\piNew{y}{(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})}]
      {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
    \NOM{Cut}
    \UIC{$\seq
      [\piNew{x}{\piNew{y}{(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})}}]
      {\tmty{z}{\one}}$}
  \end{prooftree*}
\end{center}\vspace{.5\belowdisplayskip}
